### 2016-11-04 text/ms.Rmd
Tweaks to main text

@@

A strength of superensembles is that they can be tailored to predict specific
response variables. For example, we built separate superensemble models of mean
$B/B_\mathrm{MSY}$ and the slope of $B/B_\mathrm{MSY}$. The same set of model
weights or non-linear relationships need not hold across different response
variables. For instance, SSCOM contributed little to the GBM superensemble
estimate of status at higher levels of predicted $B/B_\mathrm{MSY}$ (Fig.
\ref{partial-sim}), but contributed strongly to estimates of trend (Fig.
\ref{partial-sim-slope}). Formally, fitting superensemble models to specific
quantities of interest (such as the slope of $B/B_\mathrm{MSY}$) provides an additional
calibration step to a quantity of interest [@rykiel1996].\R{A10}
This ensemble calibration could include a loss function
tailored to the goals of the model, say placing greater weight on accuracy at
lower rather than higher status levels. Conversely, because superensembles are
tailored to a specific response and loss function, superensembles force a
modeller to choose an operational purpose for their model upfront [*sensu*
@dickey-collas2014]. For instance, one could have an ensemble 
estimate of $B$ and an ensemble estimate of $B_0$, but their
ratio may not be the same as an ensemble estimate of $B/B_0$.
A modeller might therefore choose to focus on $B/B_0$, 
which provides a unitless ratio, is easier to compare across stocks, 
and the ratio is often a more stable estimate across models [@deroba2015].

>>>>

\noindent \R{A5}For this illustrative example 
we chose this level of model complexity *a priori*
but a modeller could apply model selection via information-theoretic
or cross-validation approaches.

@@

A strength of superensembles is that they can be tailored to predict specific
response variables. For example, we built separate superensemble models of mean
$B/B_\mathrm{MSY}$ and the slope of $B/B_\mathrm{MSY}$. The same set of model
weights or non-linear relationships need not hold across different response
variables. For instance, SSCOM contributed little to the GBM superensemble
estimate of status at higher levels of predicted $B/B_\mathrm{MSY}$ (Fig.
\ref{partial-sim}), but contributed strongly to estimates of trend (Fig.
\ref{partial-sim-slope}). Formally, fitting superensemble models to specific
quantities of interest (such as the slope of $B/B_\mathrm{MSY}$) provides an additional
calibration step to a quantity of interest [@rykiel1996].\R{A10}
This ensemble calibration could include a loss function
tailored to the goals of the model, say placing greater weight on accuracy at
lower rather than higher status levels. Conversely, because superensembles are
tailored to a specific response and loss function, superensembles force a
modeller to choose an operational purpose for their model upfront [*sensu*
@dickey-collas2014]. \R{E}For instance, one could have an ensemble 
estimate of $B$ and an ensemble estimate of $B_0$, but their
ratio may not be the same as an ensemble estimate of $B/B_0$.
A modeller might therefore choose to focus on $B/B_0$, 
which provides a unitless ratio, is easier to compare across stocks, 
and the ratio is often a more stable estimate across models [@deroba2015].
